---
title: "Build Height Database"
format: html
---

## National Health and Nutrition Examination Survey

The NHANES (<https://www.cdc.gov/nchs/nhanes/index.html>) is a nationally
representative survey of the United Sates recording information about health,
nutrition, and risk factors.

## Finding the data

Since the NHANES is a large survey covering many years, we need to search
through the components to find what we want.

The demographics component has standard information about all respondents
and each respondent is uniquely identified by the sequence number variable SEQN.
The data codebook is available at <https://wwwn.cdc.gov/Nchs/Data/Nhanes/Public/2021/DataFiles/DEMO_L.htm>

The body measures component has height, weight, BMI, etc. and is linkable
to the demographics via the sequence number. The data codebook is available at
<https://wwwn.cdc.gov/Nchs/Data/Nhanes/Public/2021/DataFiles/BMX_L.htm>

To get a proper nationally representative sample, you'll need to use the survey
weights to conduct the analysis. The process is detailed at
<https://wwwn.cdc.gov/nchs/nhanes/continuousnhanes/overviewbrief.aspx?Cycle=2021-2023>

## Load the data

I've selected the relevant variables for this analysis.

```{r}
library(haven)
library(tidyverse)
library(writexl)
demographics <- read_xpt("data/DEMO_L.xpt", NULL) %>%
  select(SEQN, RIDAGEYR, RIAGENDR, RIDRETH1, RIDRETH3, WTINT2YR, WTMEC2YR)
body_measures <- read_xpt("data/BMX_L.xpt", NULL) %>% select(SEQN, BMXHT)
```

## Create the dataset

Merging both components and saving to a spreadsheet.

```{r}
population_data <- demographics %>%
  inner_join(body_measures, by = "SEQN") %>%
  write_xlsx(path = "analytic.xlsx")
```

## Generate the friends data

We will just generate the friends data by hand.

```{r}
friends <- tibble(
  name = c("Lilly", "Selena", "Fenix", "Maddie", "Silas"),
  gender = c("female", "female", NA, "female", "male"),
  height_feet = c(5, 5, 6, 5, 6),
  height_inches = c(1, 4, 0, 9, 4)
) %>%
  write_xlsx(path = "friends.xlsx")
```
